# About_US {#cross}


Cross-references make it easier for your readers to find and link to elements in your book.

## Mengna Wang

Hi, this is Mengna Wang, you can also call me Mona. I grow up from Suzhou China, a place known with a lot of rivers and bridges. I came to the United States 5 years ago, and went to high school and undergraduate at upstate NY. I always wanted to explore new places in the United States, not just for travel but actually stay there and experience everything there, because I stayed in NY for so long. I am super happy about the opportunity to study at University of Michigan, a completely different place than NY, which is kind of a dream come true opportunity hahaha, and I love here a lot so far. My goal for this year is to finish the program successfully and take the most from the program, have fun and make lots of friends!



There are two steps to cross-reference any heading:

1. Label the heading: `# Hello world {#nice-label}`. 
    - Leave the label off if you like the automated heading generated based on your heading title: for example, `# Hello world` = `# Hello world {#hello-world}`.
    - To label an un-numbered heading, use: `# Hello world {-#nice-label}` or `{# Hello world .unnumbered}`.

1. Next, reference the labeled heading anywhere in the text using `\@ref(nice-label)`; for example, please see Chapter \@ref(cross). 
    - If you prefer text as the link instead of a numbered reference use: [any text you want can go here](#cross).

## Remona Wang





Figures and tables *with captions* can also be cross-referenced from elsewhere in your book using `\@ref(fig:chunk-label)` and `\@ref(tab:chunk-label)`, respectively.




## Runze Huang


## Jennifer 





## Carlo







See Figure \@ref(fig:nice-fig).

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center', fig.alt='Plot with connected points showing that vapor pressure of mercury increases exponentially as temperature increases.'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Don't miss Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(pressure, 10), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
